A4V PCA

### 2024-03-22 A4V_BodySections_RNAseq/R code/A4V_DEG_Analyses.Rmd
overdue update

---
title: "G85R vs WT (M + F)"
author: "John Santiago"
date: "2023-07-11"
output: html_document
---

@@

```{r echo = F, include=F}
##Load Libraries

library(biomaRt)
library(org.Dm.eg.db)
library(goseq)
library(GO.db)
library(visNetwork)
library(rrvgo)
library(plotly)
library(KEGGREST)
library(pathview)
library(VennDiagram)
library(heatmaply)
```

```{r, echo = F, include = F}

##load all files from github
git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
cpmdata = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT_cpmdata.csv"),row.names = 1)
groups  = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.metadata.csv"),row.names = 1)
TKT.EdgeR = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FDRTable.csv"),row.names = 1)
TKT.EdgeR.FC = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FCTable.csv"),row.names = 1)

GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)
kegg = readRDS(gzcon(url(paste0(git.dir,"GeneralDataFiles/kegg.symbol2path.RData"))))
kegg.names = read.csv(paste0(git.dir, "GeneralDataFiles/KEGG.names.csv"), row.names = 1)

Synaptic = read.csv("/Users/johncsantiago/Documents/SynapticGenesandTFs.csv")

genesingo=as.list(org.Dm.egGO2ALLEGS)

##mean.cpm; Mean cpm for each gene in each condition (groups$Group). Used for filtering
mean.cpm = matrix(0, ncol = length(unique(groups$Group)), nrow = nrow(cpmdata))
colnames(mean.cpm) = unique(groups$Group)
row.names(mean.cpm) = row.names(cpmdata)
i=1
while(i<=ncol(mean.cpm)){
  mean.cpm[,i]= apply(cpmdata[,row.names(groups[groups$Group == colnames(mean.cpm)[i],])], 1, mean)
  i=i+1
}

i=1
for(i in 1:ncol(TKT.EdgeR)){
  TKT.EdgeR[TKT.EdgeR[,i] == 0,i] = 2
  i=i+1
}

@@

@@

##GR vs WT Females
sigs1 = row.names(TKT.EdgeR)[TKT.EdgeR[,"GRxWT.FC"] <= .05]
bg1 = row.names(TKT.EdgeR)[TKT.EdgeR[, "GRxWT.FC"]<= 1]

sigs2 = row.names(TKT.EdgeR)[TKT.EdgeR[,"GRxWT.MC"] <= .05]
bg2 = row.names(TKT.EdgeR)[TKT.EdgeR[, "GRxWT.MC"]<= 1]

sigs = intersect(sigs1, sigs2)
bg = unique(c(bg1, bg2))

sigsKEY = GeneIDKey[sigs,]
sigs = sigsKEY$Symbol
bgKEY = GeneIDKey[bg,]
bg = bgKEY$Symbol

@@

GO.data = sig.cats[["GO"]]
GO.ontology = "BP"
go_analysis = GO.data$category[GO.data$adjp <= .05 & GO.data$ontology == GO.ontology]
scores = setNames(-log10(GO.data$adjp), go_analysis)

@@

@@

##GR.F vs WT.F specific volcano

specific.cat = c('none', 'parent.category', 'specific.kegg', 'specific.go')

specific.cat = specific.cat[1]
parent.category = 'neurogenesis'
specific.kegg = "DNA replication"
specific.go =  '32553'
Synaptic.genes = F

set.size = F

GOterm.genes = vector('list', length = length(unique(reducedTerms$parent)))
names(GOterm.genes) = unique(reducedTerms$parent)
i=1
while(i<=length(GOterm.genes)){
  goinparent = reducedTerms[grep(names(GOterm.genes)[i], reducedTerms$parent),'go']
  genesinparent = unlist(genesingo[goinparent])
  GOterm.genes[[i]] = GeneIDKey[GeneIDKey$ensembl %in% genesinparent, 'FBgn']
  i = i +1
}

volcano.data = data.frame(Symbol = GeneIDKey[row.names(TKT.EdgeR), "Symbol"], 
                          FDR = -log2(TKT.EdgeR[, 'GRxWT.FC']),
                          FC = TKT.EdgeR.FC[row.names(TKT.EdgeR), 'GRxWT.FC'],
                          ##Color = 0)
                          Color = 'grey',
                          size = 5*log(mean.cpm[row.names(TKT.EdgeR),"GR.F"]),
                          GR.F.cpm = mean.cpm[row.names(TKT.EdgeR),"GR.F"],
                          WT.F.cpm = mean.cpm[row.names(TKT.EdgeR),"WT.F"],
                          GO.terms = "none")

main.title = "Significant DEG in G85R Females vs. WT Females"

volcano.data$Color[volcano.data$FDR >= -log2(.05) & volcano.data$FC < 0] = 'lightblue'
volcano.data$Color[volcano.data$FDR >= -log2(.0001) & volcano.data$FC < 0] = 'steelblue'
volcano.data$Color[volcano.data$FDR >= -log2(.000001) & volcano.data$FC < 0] = 'dodgerblue'

volcano.data$Color[volcano.data$FDR >= -log2(.05) & volcano.data$FC > 0] = 'lightcoral'
volcano.data$Color[volcano.data$FDR >= -log2(.0001) & volcano.data$FC > 0] = 'tomato'
volcano.data$Color[volcano.data$FDR >= -log2(.000001) & volcano.data$FC > 0] = 'firebrick'

volcano.data$size[volcano.data$FDR <= -log2(.05)] = 3

if(set.size == T){
  volcano.data$size = 15
  volcano.data$size[volcano.data$FDR <= -log2(.05)] = 5
}

volcano.data$Color = 'grey'
volcano.data$Color[volcano.data$Symbol %in% Synaptic$Symbol] = 'deeppink'

if(specific.cat == 'parent.category'){
  parent.genes = GOterm.genes[[intersect(reducedTerms[reducedTerms$parentTerm == parent.category, "go"], names(GOterm.genes))]]
  volcano.data$Color = 'honeydew'
  volcano.data[parent.genes, 'Color'] = 'deeppink'
  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
  main.title = sig.cats$GO[c(grep(parent.category, sig.cats$GO$term), grep(parent.category, sig.cats$GO$category)), 'term']
}

if(specific.cat == 'specific.kegg'){
  kegg.id = sig.cats$KEGG[c(grep(specific.kegg, sig.cats$KEGG$Name), grep(specific.kegg, sig.cats$KEGG$category)), 'category']
  kegg.genes = names(kegg[grep(kegg.id, kegg)])
  volcano.data$Color = 'honeydew'
  row.names(volcano.data) = volcano.data$Symbol
    volcano.data[kegg.genes, 'Color'] = 'deeppink'
  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
  main.title = sig.cats$KEGG[c(grep(specific.kegg, sig.cats$KEGG$Name), grep(specific.kegg, sig.cats$KEGG$category)), 'Name']
}

if(specific.cat == 'specific.go'){
  go.id = sig.cats$GO[c(grep(specific.go, sig.cats$GO$term), grep(specific.go, sig.cats$GO$category)), 'category']
  volcano.data$Color = 'honeydew'
  go.genes = genesingo[[go.id]]
  go.genes = GeneIDKey[GeneIDKey$ensembl %in% go.genes, "FBgn"]
  go.genes = intersect(go.genes, row.names(volcano.data))
  volcano.data[go.genes, 'Color'] = 'deeppink'
  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
  main.title = sig.cats$GO[c(grep(specific.go, sig.cats$GO$term), grep(specific.go, sig.cats$GO$category)), 'term']
}

##volcano.data

fig = plot_ly(data = volcano.data,
              x = ~FC,
              y = ~FDR,
              type = 'scatter',
              mode = 'markers',
              marker = list(color = ~Color, colors = ~Color, size = volcano.data$size,
                            line = list(color = 'black', width = .5)),
              hoverinfo = "text",
              hovertext = paste("Gene:", volcano.data$Symbol,
                      "\n-log2(FDR): ", round(volcano.data$FDR,2),
                      "\nFC: ", round(volcano.data$FC,2),
                      "\nG85R mean cpm: ", round(volcano.data$GR.F.cpm, 1),
                      "\nWT mean cpm: ", round(volcano.data$WT.F.cpm, 1)))
fig = fig %>% layout(title = main.title)

              ##color = ~Color,
              ##colors = 'Spectral')
              ##color = ~Color,
              ##colors = ~Color)
              ##marker = list(colorscale = list(c(0,.5,1), c("blue","yellow", "red")), color = ~Color))

@@

```{r}
specific.cat = c('none', 'parent.category', 'specific.kegg', 'specific.go')

specific.cat = specific.cat[1]
parent.category = 'chromosome organization'
specific.kegg = "DNA replication"
specific.go =  '006457'

set.size = F

GOterm.genes = vector('list', length = length(unique(reducedTerms$parent)))
names(GOterm.genes) = unique(reducedTerms$parent)
i=1
while(i<=length(GOterm.genes)){
  goinparent = reducedTerms[grep(names(GOterm.genes)[i], reducedTerms$parent),'go']
  genesinparent = unlist(genesingo[goinparent])
  GOterm.genes[[i]] = GeneIDKey[GeneIDKey$ensembl %in% genesinparent, 'FBgn']
  i = i +1
}

volcano.data = data.frame(Symbol = GeneIDKey[row.names(TKT.EdgeR), "Symbol"], 
                          FDR = -log2(TKT.EdgeR[, 'GRxWT.MC']),
                          FC = TKT.EdgeR.FC[row.names(TKT.EdgeR), 'GRxWT.MC'],
                          ##Color = 0)
                          Color = 'grey',
                          size = 5*log(mean.cpm[row.names(TKT.EdgeR),"GR.M"]),
                          GR.F.cpm = mean.cpm[row.names(TKT.EdgeR),"GR.M"],
                          WT.F.cpm = mean.cpm[row.names(TKT.EdgeR),"WT.M"],
                          GO.terms = "none")

main.title = "Significant DEG in G85R Males vs. WT Males"

volcano.data$Color[volcano.data$FDR >= -log2(.05) & volcano.data$FC < 0] = 'lightblue'
volcano.data$Color[volcano.data$FDR >= -log2(.0001) & volcano.data$FC < 0] = 'steelblue'
volcano.data$Color[volcano.data$FDR >= -log2(.000001) & volcano.data$FC < 0] = 'dodgerblue'

volcano.data$Color[volcano.data$FDR >= -log2(.05) & volcano.data$FC > 0] = 'lightcoral'
volcano.data$Color[volcano.data$FDR >= -log2(.0001) & volcano.data$FC > 0] = 'tomato'
volcano.data$Color[volcano.data$FDR >= -log2(.000001) & volcano.data$FC > 0] = 'firebrick'

volcano.data$size[volcano.data$FDR <= -log2(.05)] = 3

if(set.size == T){
  volcano.data$size = 15
  volcano.data$size[volcano.data$FDR <= -log2(.05)] = 5
}

if(specific.cat == 'parent.category'){
  parent.genes = GOterm.genes[[intersect(reducedTerms[reducedTerms$parentTerm == parent.category, "go"], names(GOterm.genes))]]
  volcano.data$Color = 'honeydew'
  volcano.data[parent.genes, 'Color'] = 'deeppink'
  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
  main.title = sig.cats$GO[c(grep(parent.category, sig.cats$GO$term), grep(parent.category, sig.cats$GO$category)), 'term']
}

if(specific.cat == 'specific.kegg'){
  kegg.id = sig.cats$KEGG[c(grep(specific.kegg, sig.cats$KEGG$Name), grep(specific.kegg, sig.cats$KEGG$category)), 'category']
  kegg.genes = names(kegg[grep(kegg.id, kegg)])
  volcano.data$Color = 'honeydew'
  row.names(volcano.data) = volcano.data$Symbol
    volcano.data[kegg.genes, 'Color'] = 'deeppink'
  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
  main.title = sig.cats$KEGG[c(grep(specific.kegg, sig.cats$KEGG$Name), grep(specific.kegg, sig.cats$KEGG$category)), 'Name']
}

if(specific.cat == 'specific.go'){
  go.id = sig.cats$GO[c(grep(specific.go, sig.cats$GO$term), grep(specific.go, sig.cats$GO$category)), 'category']
  volcano.data$Color = 'honeydew'
  go.genes = genesingo[[go.id]]
  go.genes = GeneIDKey[GeneIDKey$ensembl %in% go.genes, "FBgn"]
  go.genes = intersect(go.genes, row.names(volcano.data))
  volcano.data[go.genes, 'Color'] = 'deeppink'
  volcano.data = volcano.data[order(volcano.data$Color, decreasing = T),]
  main.title = sig.cats$GO[c(grep(specific.go, sig.cats$GO$term), grep(specific.go, sig.cats$GO$category)), 'term']
}

##volcano.data

fig = plot_ly(data = volcano.data,
              x = ~FC,
              y = ~FDR,
              type = 'scatter',
              mode = 'markers',
              marker = list(color = ~Color, colors = ~Color, size = volcano.data$size,
                            line = list(color = 'black', width = .5)),
              hoverinfo = "text",
              hovertext = paste("Gene:", volcano.data$Symbol,
                      "\n-log2(FDR): ", round(volcano.data$FDR,2),
                      "\nFC: ", round(volcano.data$FC,2),
                      "\nG85R mean cpm: ", round(volcano.data$GR.F.cpm, 1),
                      "\nWT mean cpm: ", round(volcano.data$WT.F.cpm, 1)))
fig = fig %>% layout(title = main.title)

@@

@@

rawdata = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/MetabolomicsForMetaboanalyst.txt", sep = "\t", row.names = 1)

KEGG.Key = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/Metabolomics/RawMetabolomicData.csv", row.names = 1)
KEGG.Key = setNames(KEGG.Key[-c(1:2), 2], row.names(KEGG.Key)[-c(1:2)])

genotypes = setNames(c("WT", "GR", "TktOEWT", "TktOEGR", "TktDfWT", "TktDfGR"), c("C", "E", "A", "F", "B", "D"))

metadata = data.frame(Sample = colnames(rawdata), 
                      Group = as.character(rawdata[1,]), 
                      TIC = as.numeric(rawdata[2,]), 
                      Genotypes = genotypes[as.character(rawdata[1,])])

norm.func = function(data){
  nd = (as.numeric(data)/metadata$TIC)*1000
  return(nd)
}

norm.data = t(apply(rawdata[3:nrow(rawdata),], 1, norm.func))
colnames(norm.data) = colnames(rawdata)

group.mean=function(data){
  gm = mean(na.omit(data))
}

mean.data = matrix(0, nrow=nrow(norm.data), ncol = length(genotypes))
row.names(mean.data) = row.names(norm.data)
colnames(mean.data) = unique(metadata$Group)

i=1
while(i<=ncol(mean.data)){
  mean.data[,i] = apply(norm.data[,metadata[metadata$Group == colnames(mean.data)[i], "Sample"]], 1, group.mean)
  i = i+1
}

compare.conditions = function(condition1, condition2){
  columns1 = metadata[metadata$Group == condition1, "Sample"]
  columns2 = metadata[metadata$Group == condition2, "Sample"]
  p=setNames(rep(NA, nrow(norm.data)), row.names(norm.data))
  i=1
  while(i<=length(p)){
    if(length(na.omit(norm.data[i,columns1]))>2 & 
       length(na.omit(norm.data[i,columns2]))>2){
      temp = t.test(na.omit(norm.data[i,columns1]),
                    na.omit(norm.data[i,columns2]), paired = F, var.equal = T)
      p[i] = temp[[3]]
      }
    i=i+1
    }

  fdr = p.adjust(p, "BH", length(p))

  fc = mean.data[,condition1]/mean.data[,condition2]

  comparison.table = data.frame(p = p, 
                                FDR = fdr, 
                                FC = fc, 
                                KEGG = KEGG.Key[row.names(mean.data)])

  comparison.table = comparison.table[order(comparison.table$FDR),]
}

GRxWT.C = compare.conditions("E", "C")
GRxWT.Df = compare.conditions("D", "B")
GRxWT.OE = compare.conditions("F", "A")

set.size == F
volcano.data = data.frame(Symbol = row.names(GRxWT.C), 
                          FDR = -log2(GRxWT.C$FDR),
                          FC = log2(GRxWT.C$FC),
                          Color = 'honeydew',
                          size = log(mean.data[row.names(GRxWT.C),'E']),
                          GR.Level = mean.data[row.names(GRxWT.C), "E"],
                          WT.Level = mean.data[row.names(GRxWT.C), "C"],
                          GO.terms = "none")

main.title = "FC for metabolites in G85R vs. WT"

volcano.data$Color[volcano.data$FDR >= -log2(.05) & volcano.data$FC < 0] = 'lightblue'
volcano.data$Color[volcano.data$FDR >= -log2(.0001) & volcano.data$FC < 0] = 'steelblue'
volcano.data$Color[volcano.data$FDR >= -log2(.000001) & volcano.data$FC < 0] = 'dodgerblue'

volcano.data$Color[volcano.data$FDR >= -log2(.05) & volcano.data$FC > 0] = 'lightcoral'
volcano.data$Color[volcano.data$FDR >= -log2(.0001) & volcano.data$FC > 0] = 'tomato'
volcano.data$Color[volcano.data$FDR >= -log2(.000001) & volcano.data$FC > 0] = 'firebrick'

##volcano.data$size[volcano.data$FDR <= -log2(.05)] = 3

if(set.size == T){
  volcano.data$size = 15
  volcano.data$size[volcano.data$FDR <= -log2(.05)] = 5
}

fig = plot_ly(data = volcano.data,
              x = ~FC,
              y = ~FDR,
              type = 'scatter',
              mode = 'markers',
              marker = list(color = ~Color, colors = ~Color, size = volcano.data$size,
                            line = list(color = 'black', width = .5)),
              hoverinfo = "text",
              hovertext = paste("Metabolite:", volcano.data$Symbol,
                      "\n-log2(FDR): ", round(volcano.data$FDR,2),
                      "\nFC: ", round(volcano.data$FC,2),
                      "\nG85R mean cpm: ", round(volcano.data$GR.Level, 1),
                      "\nWT mean cpm: ", round(volcano.data$WT.Level, 1)))
fig = fig %>% layout(title = main.title)

@@

```{r, include = F, echo = F}

if(intersect(list.files(), "KEGG_Image_Files") != "KEGG_Image_Files"){
  dir.create(paste0(dirname(rstudioapi::getSourceEditorContext()$path), "/KEGG_Image_Files/"))
}

Home = dirname(rstudioapi::getSourceEditorContext()$path)
OutputDir = paste0(Home, "/KEGG_Image_Files/")

ShowKEGG = function(PathwayID){

download.kegg(pathway.id= PathwayID, species = "dme", kegg.dir = OutputDir)
xml.file=paste0(OutputDir, "dme",PathwayID,".xml")
node.data=node.info(xml.file)

all.path = names(kegg[grep(PathwayID,kegg)])

up = TKT.EdgeR.FC[TKT.EdgeR.FC$Moderate == 1, "Symbol"]
Moderate = intersect(Moderate, all.path)
Moderate = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% Moderate, "CG"],sep="")

Strong = Df.data[Df.data$Strong == 1, "Symbol"]
Strong = intersect(Strong, all.path)
Strong = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% Strong, "CG"],sep="")

Enhancer = Df.data[Df.data$Enhancer == 1, "Symbol"]
Enhancer = intersect(Enhancer, all.path)
Enhancer = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% Enhancer, "CG"],sep="")

Lethal = Df.data[Df.data$Lethal == 1, "Symbol"]
Lethal = intersect(Lethal, all.path)
Lethal = paste("Dmel_", GeneIDKey[GeneIDKey$Symbol %in% Strong, "CG"],sep="")

>>>>

---
title: "A4V PCA"
author: "John Santiago"
date: "2024-01-22"
output: html_document
---

@@

```{r echo=F, include=F}

library(plotly)
library(edgeR)
library(goseq)
library(org.Dm.eg.db)
library(rrvgo)
library(VennDiagram)

cpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.cpmdata.csv", row.names = 1)

meancpm = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.meancpmdata.csv", row.names = 1)

FDR = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.FDRdata.csv", row.names = 1)

FC = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.FCdata.csv", row.names = 1)

meta = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/A4V_BodySections_RNAseq/A4V.metadata.csv", row.names = 1)

GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)

@@

```{r echo = F}

sigsA3FvMT = row.names(FDR)[FDR[,'A3FvMT']<.05]
sigsS3FvMT = row.names(FDR)[FDR[,'S3FvMT']<.05]
sigsA9FvMT = row.names(FDR)[FDR[,'A9FvMT']<.05]
sigsS9FvMT = row.names(FDR)[FDR[,'S9FvMT']<.05]

GR.cpm = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT_cpmdata.csv"),row.names = 1)
GR.meta  = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.metadata.csv"),row.names = 1)
GR.FDR = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FDRTable.csv"),row.names = 1)

sigsGR.FxM = row.names(GR.FDR)[GR.FDR$GR.FxM <.05]
sigsWT.FxM = row.names(GR.FDR)[GR.FDR$WT.FxM <.05]

A3 = setdiff(sigsA3FvMT, sigsS3FvMT)
A9 = setdiff(sigsA9FvMT, sigsS9FvMT)
GR = setdiff(sigsGR.FxM, sigsWT.FxM)

##Sample titles as strings. Only fill in up to your number of selected categories
set1="A4V 3-day"
set2="A4V 9-day"
set3="G85R Larvae"
set4=""

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1=A3
s2=A9
s3=GR
s4=""

T3 = A3
T9 = A9

##Triple Venn
grid.newpage()
draw.triple.venn(area1=length(s1),area2=length(s2),area3=length(s3),n12=length(intersect(s1,s2)),n23 = length(intersect(s2,s3)),n13 = length(intersect(s1,s3)),n123 = length(intersect(intersect(s1,s2),s3)),category=c(set1,set2,set3),fill = c("green", "blue","red"),cex=1.5,cat.cex = 1)

```{r echo = F}

sigsA3FvMH = row.names(FDR)[FDR[,'A3FvMH']<.05]
sigsS3FvMH = row.names(FDR)[FDR[,'S3FvMH']<.05]
sigsA9FvMH = row.names(FDR)[FDR[,'A9FvMH']<.05]
sigsS9FvMH = row.names(FDR)[FDR[,'S9FvMH']<.05]

GR.cpm = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT_cpmdata.csv"),row.names = 1)
GR.meta  = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.metadata.csv"),row.names = 1)
GR.FDR = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FDRTable.csv"),row.names = 1)

sigsGR.FxM = row.names(GR.FDR)[GR.FDR$GR.FxM <.05]
sigsWT.FxM = row.names(GR.FDR)[GR.FDR$WT.FxM <.05]

A3 = setdiff(sigsA3FvMH, sigsS3FvMH)
A9 = setdiff(sigsA9FvMH, sigsS9FvMH)
GR = setdiff(sigsGR.FxM, sigsWT.FxM)

##Sample titles as strings. Only fill in up to your number of selected categories
set1="A4V 3-day"
set2="A4V 9-day"
set3="G85R Larvae"
set4=""

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1=A3
s2=A9
s3=GR
s4=""

H3=A3
H9=A9

##Triple Venn
grid.newpage()
draw.triple.venn(area1=length(s1),area2=length(s2),area3=length(s3),n12=length(intersect(s1,s2)),n23 = length(intersect(s2,s3)),n13 = length(intersect(s1,s3)),n123 = length(intersect(intersect(s1,s2),s3)),category=c(set1,set2,set3),fill = c("green", "blue","red"),cex=1.5,cat.cex = 1)

```{r echo = F}

sigsA3FvMA = row.names(FDR)[FDR[,'A3FvMA']<.05]
sigsS3FvMA = row.names(FDR)[FDR[,'S3FvMA']<.05]
sigsA9FvMA = row.names(FDR)[FDR[,'A9FvMA']<.05]
sigsS9FvMA = row.names(FDR)[FDR[,'S9FvMA']<.05]

GR.cpm = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT_cpmdata.csv"),row.names = 1)
GR.meta  = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.metadata.csv"),row.names = 1)
GR.FDR = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FDRTable.csv"),row.names = 1)

sigsGR.FxM = row.names(GR.FDR)[GR.FDR$GR.FxM <.05]
sigsWT.FxM = row.names(GR.FDR)[GR.FDR$WT.FxM <.05]

A3 = setdiff(sigsA3FvMA, sigsS3FvMA)
A9 = setdiff(sigsA9FvMA, sigsS9FvMA)
GR = setdiff(sigsGR.FxM, sigsWT.FxM)

##Sample titles as strings. Only fill in up to your number of selected categories
set1="A4V 3-day"
set2="A4V 9-day"
set3="G85R Larvae"
set4=""

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1=A3
s2=A9
s3=GR
s4=""

A3=A3
A9=A9

##Triple Venn
grid.newpage()
draw.triple.venn(area1=length(s1),area2=length(s2),area3=length(s3),n12=length(intersect(s1,s2)),n23 = length(intersect(s2,s3)),n13 = length(intersect(s1,s3)),n123 = length(intersect(intersect(s1,s2),s3)),category=c(set1,set2,set3),fill = c("green", "blue","red"),cex=1.5,cat.cex = 1)

@@

sigs = setdiff(setdiff(T9,T3),GR)
bg = row.names(FDR)

sigsKEY = GeneIDKey[sigs,]
sigs = na.omit(sigsKEY$Symbol)
bgKEY = GeneIDKey[bg,]
bg = na.omit(bgKEY$Symbol)

@@

GO.data = sig.cats[["GO"]]
GO.ontology = "BP"
go_analysis = GO.data$category[GO.data$over_represented_pvalue <= .005 & GO.data$ontology == GO.ontology]
scores = setNames(-log10(GO.data$over_represented_pvalue), go_analysis)

@@

```{r echo=F, include=F}

pca <- prcomp(t(A4V.cpm), scale.=TRUE) 
gr <- colnames(A4V.cpm)
PC1=scale(pca$x[,1])
PC2=scale(pca$x[,2])
eigs <- pca$sdev^2
ve=signif(((eigs / sum(eigs))*100)[1:3],4)

    pca.data=data.frame(Sample=gr,
                        ##PC1=scale(pca$x[,1]),
                        ##PC2=scale(pca$x[,2]),
                        PC1=scale(pca$x[,1]),
                        PC2=scale(pca$x[,2]),
                        sdev=pca$sdev,
                        Genotype=substr(gr, 1, 1), 
                        Sex=substr(gr, nchar(gr)-2, nchar(gr)-2), 
                        Age=substr(gr, 2, nchar(gr)-3),
                        Percent1=ve[1],
                        Percent2=ve[2],
                        Group= paste0(substr(gr, 1, 1),
                                      substr(gr, nchar(gr)-2, nchar(gr)-1)),
                        pca.color = substr(gr, nchar(gr)-1, nchar(gr)-1),
                        pca.shape = substr(gr, nchar(gr)-2, nchar(gr)-2))

fig  = plot_ly(data = pca.data, 
                 x = ~PC1, 
                 y = ~PC2,
                 name = ~Group,
                 type = 'scatter',
                 mode = 'markers',
                 showlegend = T,
                 color = ~pca.color,
                 symbol = ~pca.shape,
                 ##symbols = as.character(seq_along(unique(point.data$Set))),
                 ##colors = c(input$color1, input$color2, input$color3)[c(1:length(levels(pca.color)))],
                 marker = list(size = 15,
                               line = list(color = "black", width = 1.5)),
                 hoverinfo = "text",
                 hovertext = paste("Sample:", pca.data$Sample)) %>%
    layout(xaxis = list(title = paste0("PC 1", "(", pca.data$Percent1[1], "%)")),
           yaxis = list(title = paste0("PC 2", "(", pca.data$Percent2[2], "%)")))
```

@@

@@

```{r echo=F, include=F}

pca.data = cpmdata[,substr(colnames(cpmdata), nchar(colnames(cpmdata))-1, nchar(colnames(cpmdata))-1) == "H"]

remove = apply(pca.data, MARGIN = 1, sum) != 0

pca.data = pca.data[remove,]

pca <- prcomp(t(pca.data), scale.=TRUE) 
gr <- colnames(pca.data)
PC1=scale(pca$x[,1])
PC2=scale(pca$x[,2])
eigs <- pca$sdev^2
ve=signif(((eigs / sum(eigs))*100)[1:3],4)

    pca.data=data.frame(Sample=gr,
                        ##PC1=scale(pca$x[,1]),
                        ##PC2=scale(pca$x[,2]),
                        PC1=scale(pca$x[,1]),
                        PC2=scale(pca$x[,2]),
                        sdev=pca$sdev,
                        Genotype=substr(gr, 1, 1), 
                        Sex=substr(gr, nchar(gr)-2, nchar(gr)-2), 
                        Age=substr(gr, 2, nchar(gr)-3),
                        Percent1=ve[1],
                        Percent2=ve[2],
                        Group= paste0(substr(gr, 1, 1),
                                      substr(gr, nchar(gr)-2, nchar(gr)-1)))

fig  = plot_ly(data = pca.data, 
                 x = ~PC1, 
                 y = ~PC2,
                 name = ~Group,
                 type = 'scatter',
                 mode = 'markers',
                 showlegend = T,
                 color = ~Group,
                 symbol = ~Genotype,
                 ##symbols = as.character(seq_along(unique(point.data$Set))),
                 ##colors = c(input$color1, input$color2, input$color3)[c(1:length(levels(pca.color)))],
                 marker = list(size = 15,
                               line = list(color = "black", width = 1.5)),
                 hoverinfo = "text",
                 hovertext = paste("Sample:", pca.data$Sample)) %>%
    layout(xaxis = list(title = paste0("PC 1", "(", pca.data$Percent1[1], "%)")),
           yaxis = list(title = paste0("PC 2", "(", pca.data$Percent2[2], "%)")))
```

@@

```{r echo=F, include=F}

pca.data = cpmdata[,substr(colnames(cpmdata), nchar(colnames(cpmdata))-1, nchar(colnames(cpmdata))-1) == "T"]

remove = apply(pca.data, MARGIN = 1, sum) != 0

pca.data = pca.data[remove,]

pca <- prcomp(t(pca.data), scale.=TRUE) 
gr <- colnames(pca.data)
PC1=scale(pca$x[,1])
PC2=scale(pca$x[,2])
eigs <- pca$sdev^2
ve=signif(((eigs / sum(eigs))*100)[1:3],4)

    pca.data=data.frame(Sample=gr,
                        ##PC1=scale(pca$x[,1]),
                        ##PC2=scale(pca$x[,2]),
                        PC1=scale(pca$x[,1]),
                        PC2=scale(pca$x[,2]),
                        sdev=pca$sdev,
                        Genotype=substr(gr, 1, 1), 
                        Sex=substr(gr, nchar(gr)-2, nchar(gr)-2), 
                        Age=substr(gr, 2, nchar(gr)-3),
                        Percent1=ve[1],
                        Percent2=ve[2],
                        Group= paste0(substr(gr, 1, 1),
                                      substr(gr, nchar(gr)-2, nchar(gr)-1)))

fig  = plot_ly(data = pca.data, 
                 x = ~PC1, 
                 y = ~PC2,
                 name = ~Group,
                 type = 'scatter',
                 mode = 'markers',
                 showlegend = T,
                 color = ~Group,
                 symbol = ~Genotype,
                 ##symbols = as.character(seq_along(unique(point.data$Set))),
                 ##colors = c(input$color1, input$color2, input$color3)[c(1:length(levels(pca.color)))],
                 marker = list(size = 15,
                               line = list(color = "black", width = 1.5)),
                 hoverinfo = "text",
                 hovertext = paste("Sample:", pca.data$Sample)) %>%
    layout(xaxis = list(title = paste0("PC 1", "(", pca.data$Percent1[1], "%)")),
           yaxis = list(title = paste0("PC 2", "(", pca.data$Percent2[2], "%)")))
```

@@

@@

```{r echo=F, include=F}

pca.data = A4V.cpm[,substr(colnames(A4V.cpm), nchar(colnames(A4V.cpm))-1, nchar(colnames(A4V.cpm))-1) == "A"]

remove = apply(pca.data, MARGIN = 1, sum) != 0

pca.data = pca.data[remove,]

pca <- prcomp(t(pca.data), scale.=TRUE) 
gr <- colnames(pca.data)
PC1=scale(pca$x[,1])
PC2=scale(pca$x[,2])
eigs <- pca$sdev^2
ve=signif(((eigs / sum(eigs))*100)[1:3],4)

    pca.data=data.frame(Sample=gr,
                        ##PC1=scale(pca$x[,1]),
                        ##PC2=scale(pca$x[,2]),
                        PC1=scale(pca$x[,1]),
                        PC2=scale(pca$x[,2]),
                        sdev=pca$sdev,
                        Genotype=substr(gr, 1, 1), 
                        Sex=substr(gr, nchar(gr)-2, nchar(gr)-2), 
                        Age=substr(gr, 2, nchar(gr)-3),
                        Percent1=ve[1],
                        Percent2=ve[2],
                        Group= paste0(substr(gr, 1, 1),
                                      substr(gr, nchar(gr)-2, nchar(gr)-1)))
